Towards Performance-portable Parallel Programming in Computer Science Education

### 2020-01-21 src/2.Kokkos.tex

A programming model is an abstract representation of a computer. It defines a paradigm and a programming language. The programming language is used by the programmer to write source code, a human-readable textual representation of instructions and data. Source code is a sequential listing of statements evaluated from the top to bottom, one line at a time. While such ordering seems natural to describe an algorithm as it corresponds to sequential processing (both, reading code and progressing the program counter follow a time line), it does not include the notion of concurrency.

>>>>

A programming model is an abstract representation of a computer. It defines a paradigm and a programming language. The programming language is used by the programmer to write source code, a human readable, textual representation of instructions and data. Source code is a sequential listing of statements evaluated from the top to bottom, one line at a time. While such ordering seems natural to describe an algorithm as it corresponds to sequential processing (both, reading code and progressing the program counter following a time line), it does not include the notion of concurrency.
